Clicks and Cliques

### 2018-12-22 papersoul.Rnw
small changes

<<moving, dependson='data', echo=FALSE,results='asis', cache=FALSE>>=
soul %>% 
  mutate(Q5 = recode_factor(Q5, "(DK)" = "Non Response", 
    "(Refused)" = "Non Response",
    "Move outside of (answer from Sc) but stay in the state" = "Move from your neighborhood",
    "Move outside of this communitybut stay in the state" = "Move from your neighborhood",
    "Move to another city and state altogether" = "Move from your neighborhood",
    "Move to another neighborhood in (answer from Sc)" = "Move from your neighborhood", 
    "Move to another neighborhood in this community" = "Move from your neighborhood")) %>%  
  filter(!is.na(PROJWT)) %>% 
  mutate(pr = PROJWT/3)  %>% 
  svydesign(ids=~1, strata=~QSB, weights=~pr, data=.) %>% 
  svyby(~Q5,~CCEGRP2, design = ., svymean,keep.var=FALSE, na.rm=T) %>% 
  ftable() %>% data.frame() %>% 
  mutate( Var2 = gsub('statistic.Q5', '', Var2) ) %>% 
  spread(CCEGRP2, Freq) %>%  
  xtable(caption='Willingness to move outside your neighborhood', label='move') %>% 
  print(caption.placement='top')

>>>>

<<moving, dependson='data', echo=FALSE,results='asis', cache=FALSE>>=
soul %>% 
  mutate(Q5 = recode_factor(Q5, "(DK)" = "Non Response", 
    "(Refused)" = "Non Response",
    "Move outside of (answer from Sc) but stay in the state" = "Move from your neighborhood",
    "Move outside of this communitybut stay in the state" = "Move from your neighborhood",
    "Move to another city and state altogether" = "Move from your neighborhood",
    "Move to another neighborhood in (answer from Sc)" = "Move from your neighborhood", 
    "Move to another neighborhood in this community" = "Move from your neighborhood")) %>%  
  filter(!is.na(PROJWT)) %>% 
  mutate(pr = PROJWT/3)  %>% 
  svydesign(ids =~1, strata =~QSB, weights =~pr, data = .) %>% 
  svyby(~Q5,~CCEGRP2, design = ., svymean,keep.var = FALSE, na.rm = T) %>% 
  ftable() %>% data.frame() %>% 
  mutate( Var2 = gsub('statistic.Q5', '', Var2) ) %>% 
  spread(CCEGRP2, Freq) %>%  
  xtable(caption = 'Willingness to move outside your neighborhood', label = 'move') %>% 
  print(caption.placement = 'top')
